Static and Dynamic Bethe-Salpeter Equations in the $T$-Matrix Approximation

### 2022-02-05 Manuscript/Tmatrix.tex
BeH2

\title{Static and Dynamic Bethe-Salpeter Equations in the $T$-Matrix Approximation}
\author{Pierre-Fran\c{c}ois \surname{Loos}}
	\email{loos@irsamc.ups-tlse.fr}
	\affiliation{\LCPQ}
%\author{Roberto Orlando}
%	\affiliation{\LCPQ}
%	\affiliation{\LPT}
\author{Pina Romaniello}
	\email{romaniello@irsamc.ups-tlse.fr}
	\affiliation{\LPT}
	\affiliation{\ETSF}

@@

First, we study the excited states of the hydrogen molecule \ce{H2} upon dissociation.
Examples: hydrogem molecules, breaking the double bond of ethylene, BeH2,

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Excited states of the hydrogen molecule}
\label{sec:h2}
%%%%%%%%%%%%%%%%%%%%%%

%%% FIGURE 1 %%%
\begin{figure*}
	\includegraphics[width=\textwidth]{H2}
	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{H2} as a function of the interelectronic distance $R_{\ce{H-H}}$ (in \si{\angstrom}) obtained at the FCI/cc-pVDZ (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels.}
\end{figure*}
%%% %%% %%% %%%
%%%%%%%%%%%%%%%%%%%%%%
\subsection{Diatomics}
\label{sec:diatomics}
%%%%%%%%%%%%%%%%%%%%%%

%%% TABLE I %%%
\begin{table*}
	\begin{ruledtabular}
		\begin{tabular}{lcccccc}
					&			&	\mc{5}{c}{Methods}																\\
			\cline{3-7}
			Mol.	&	State	&	CIS		&	CIS(D)	&	TDHF	&	BSE@$GW$	&	BSE@$GT$	\\
			\hline
			\ce{H2}	&			&	\\
			\ce{LiH}	&			&	\\
			\ce{LiF}	&			&	\\
			\ce{BF}	&			&	\\
			\ce{CO}	&			&	\\
			\ce{N2}	&			&	\\
			\ce{F2}	&			&	\\
			\ce{FH}	&			&	\\
		\end{tabular}
	\end{ruledtabular}
\end{table*}
%%% %%% %%% %%%

@@

>>>>

\title{Static and Dynamic Bethe-Salpeter Equations in the $T$-Matrix Approximation}
\author{Pierre-Fran\c{c}ois \surname{Loos}}
	\email{loos@irsamc.ups-tlse.fr}
	\affiliation{\LCPQ}
\author{Pina Romaniello}
	\email{romaniello@irsamc.ups-tlse.fr}
	\affiliation{\LPT}
	\affiliation{\ETSF}

@@

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Excited states of the hydrogen molecule}
\label{sec:h2}
%%%%%%%%%%%%%%%%%%%%%%
As a first didactical example, we consider the excited states of the hydrogen molecule \ce{H2} and the variation of the excitation energies upon dissociation.
The excitation energies for some low-lying singlet and triplet excited states are represented in Fig.~\ref{fig:H2} as a function of the internuclear distance $R_{\ce{H-H}}$ at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.

%%% FIGURE 1 %%%
\begin{figure*}
	\includegraphics[width=\textwidth]{H2}
	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{H2} as a function of the internuclear distance $R_{\ce{H-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels with the cc-pVTZ basis.
	Raw data are reported in {\SupInf}.}
	\label{fig:H2}
\end{figure*}
%%% %%% %%% %%%

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Excited states of beryllium hydride}
\label{sec:beh2}
%%%%%%%%%%%%%%%%%%%%%%

%%% FIGURE 2 %%%
\begin{figure*}
	\includegraphics[width=\textwidth]{BeH2}
	\caption{Singlet (left) and triplet (right) excitation energies (in \si{\eV}) of \ce{BeH2} as a function of the distance $R_{\ce{Be-H}}$ (in \si{\angstrom}) computed at the FCI (black), BSE@$G_0W_0$ (blue), and BSE@$G_0T_0$ (red) levels.
	The dynamically-corrected BSE excitation energies are represented as thin lines for dBSE@$G_0W_0$ (blue), and dBSE@$G_0T_0$ (red) with the cc-pVDZ basis.
	Raw data are reported in {\SupInf}.}
	\label{fig:H2}
\end{figure*}
%%% %%% %%% %%%

%%%%%%%%%%%%%%%%%%%%%%
\subsection{Diatomics}
\label{sec:diatomics}
%%%%%%%%%%%%%%%%%%%%%%

%%% TABLE I %%%
\begin{table*}
	\caption{Singlet and triplet excitation energies (in \si{\eV}) of various molecular systems at equilibrium geometry computed at various levels of theory with the cc-pVDZ basis set.
	The corresponding experimental equilibrium geometries have been extracted from the computational chemistry comparison and benchmark database (CCCBDB) at \url{https://cccbdb.nist.gov}.}
	\label{fig:mol}
	\begin{ruledtabular}
		\begin{tabular}{lcccccccc}
					&			&	\mc{5}{c}{Methods}																\\
			\cline{3-7}
			Mol.	&	State	&	CIS		&	CIS(D)	&	TDHF	&	BSE@$GW$	&	dBSE@$GW$	&	BSE@$GT$	&	dBSE@$GT$	\\
			\hline
			\ce{H2}	&			&	\\
			\ce{LiH}	&			&	\\
			\ce{LiF}	&			&	\\
			\ce{BF}	&			&	\\
			\ce{CO}	&			&	\\
			\ce{N2}	&			&	\\
			\ce{F2}	&			&	\\
			\ce{FH}	&			&	\\
		\end{tabular}
	\end{ruledtabular}
\end{table*}
%%% %%% %%% %%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{acknowledgements}
The authors thank Roberto Orlando for useful discussions.
PFL thanks the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (Grant agreement No.~863481) for funding.
This project has also received financial support from the CNRS through the 80|Prime program and has been supported through the EUR grant NanoX ANR-17-EURE-0009 in the framework of the ``Programme des Investissements d’Avenir''.
\end{acknowledgements}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
%\appendix
%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%
%\section{$T$-matrix self-energy in the spatial orbital basis}
%%%%%%%%%%%%%%%%%%%%%%%%

%Here, we provide implementable expressions for the $T$-matrix self-energy in the spatial orbital basis.
